paper1_figures

### 2023-10-10 paper1_figures.Rmd
10.10

FIGURE 1: diagram of papers' selection process
``` {r}
library(DiagrammeR)
library(webshot)
DiagrammeR::grViz("digraph {
graph [layout = dot, rankdir = TB]

node [shape = rectangle]        
rec1 [label = 'Papers identified from search engines
n = 5210']
rec2 [label = 'Duplicates
n = 624']
rec3 [label = 'Papers screened based on titles and abstracts
n = 4586']
rec4 [label = 'Papers not suitable
n = 4333']
rec5 [label = 'Papers read completely
n = 253']
rec6 [label = 'Papers not suitable
n = 157']
rec7 [label = 'Studies included
n = 96']

@@

>>>>

FIGURE 1: diagram of papers' selection process
``` {r}
library(DiagrammeR)
library(webshot)
DiagrammeR::grViz("digraph {
graph [layout = neato, rankdir = TB]

node [shape = rectangle]        
rec1 [label = 'Papers identified from search engines
n = 5210', pos='0,0!']
rec2 [label = 'Duplicates
n = 624', pos='3,0!']
rec3 [label = 'Papers screened based on titles and abstracts
n = 4586', pos='0,-1!']
rec4 [label = 'Papers not suitable
n = 4333', pos='3,-1!']
rec5 [label = 'Papers read completely
n = 253', pos='0,-2!']
rec6 [label = 'Papers not suitable
n = 157', pos='3,-2!']
rec7 [label = 'Studies included
n = 96', pos='0,-3!']

@@

``` {r}
library(DiagrammeR)
library(webshot)
DiagrammeR::grViz("digraph {
  graph [layout = fdp, rankdir = LR]

  node [shape = rectangle]
  rec1 [label = 'social identity', pos='0,0!']
  rec2 [label = 'cooperation', pos='4,0!']
  rec3 [label = 'social norms']
  rec4 [label = 'communication']
  rec5 [label = 'trust']

  rec1 -> rec2
  rec1 -> rec3 -> rec2
  rec4 -> rec3
  rec4 -> rec1
  rec1 -> rec5 -> rec2
}", height = 500)
```

### 2023-10-10 paper1_markdown.Rmd
10.10

PRISMA-ScR:

-   Describe the rationale for the review in the context of what is already known. Explain why the review questions/objectives lend themselves to a scoping review approach

    many studies on cooperation, but just a few focus on commons =\> similar aspects between commons and social dilemmas, so literature on social dilemma can be a powerful tool to investigate which factors could impact cooperation in commons

-   Provide an explicit statement of the questions and objectives being addressed with reference to their key elements (e.g., population or participants, concepts, and context) or other relevant key elements used to conceptualize the review questions and/or objectives.

PLAN OF THE INTRODUCTION:

-   COMMONS: what they are, why they become more and more popular and their main challenge = cooperation

    -   commons' definition

    -   more and more interest in commons because they could be a solution (see @Pacheco2014)

    -   cooperation =\> provide example of the Tragedy of the Commons

In a commons situation individual, short-term interests are at odds with collective, long-term ones [@Hardin1968]. To ensure the success of a commons, people have therefore to sacrifice a part of their personal benefits for the collective good. For instance, a fisher could be tempted to fish in large quantity from a common basin, but if every other fisher did the same, fishes would not be enough to reproduce, and therefore there would be less fish for the following season.

Cooperation, defined as a personal sacrifice for the greater good [@Kollock1998], is thus essential to in commons, and that is why a deeper understanding of how it works in this context is essential. Cooperation has often been studied with social dilemma experiments XXX.

=\> existing literature on cooperation =\> retake the text below

-   cooperation: often studied in social dilemma situation, while there is a lack of (quantitative) studies in commons

-   similarities between commons and social dilemma, that justify why taking SD to investigate commons is pertinent + to make the link: list of papers that studied a common in a social dilemma perspective (ex: Hartl & Hofmann, 2022)

**once selected the journal, re-organize all the introduction!!!**

Many societal problems that humans are facing nowadays have a social dilemma structure [@Kollock1998], i. e. they are situations in which short-term, individual interests are at odds with long-term, collective ones [@Hardin1968]. More specifically, in such situations, each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do. However, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980].

An example of real-life social dilemma is the climate crisis that we are actually facing: engaging in pro-environmental behaviours to reduce our ecological footprint is often more complicated and less advantageous for the self than acting without worrying about environment [@Griskevicius2010]. However, since behaviours that serve our personal well-being tend to be detrimental to the environment [@VanLange1998], if everyone defects by choosing the easy way, consequences will be (and already are) catastrophic. Another (less tragic) example is provided by @Kollock1998 and involves public television: the best outcome at the individual level would be to have access to the programs without paying the fee, but if nobody paid it, public television would no longer exist. Cooperation (i.e. sacrificing for the grater good at a personal cost, [@Kollock1998]) is therefore essential to avoid the worst collective outcome in social dilemma situations, and that is why a deep comprehension of this phenomenon is needed.

Classical economic theories have described human being as "homo economicus". This means that, facing a choice, individuals are considered as completely rational and always maximizing (expected) utility [@Edwards1954]. Therefore, according to these theories, individuals are not supposed to show altruistic behaviours, defined as behaviours that involve costs for the self while benefiting others [@Wittek2015]. However, there are individual differences in the level of rationality, i.e. the ability to think analytically at the situation. @Lang2018 showed that individuals scoring low in rationality cooperated more than individuals with an high score. This shows that, when investigating a phenomenon like cooperation, individual differences must be taken into account.

Another theoretical approach toward cooperation is the evolutionary perspective, who suggests that individuals can show cooperation, but only when doing so bring them a personal advantage. For example, the theory of competitive altruism [@Roberts1998] says that acting for the others' good could be a signal of a person's pro-sociality, and therefore improve this person's reputation. Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995]. @VanVugt2010a confirmed this assumptions in a social dilemma setting, by showing that people contributed more to a public resource when their action was visible by others, even if the public good was already provided or unattainable. In lines with hypothesis, participants who wasted their resources in the public good were perceived with an higher social status. This means that cooperation can also serve a self-interested goal, by improving the reputation of cooperators.

According to economic and evolutionary theories, individuals are always pursuing their self-interest, either by maximizing their personal payoff by defecting, either by cooperating to increase their social status and reputation. However, in social dilemma experiments, a significant amount of people are "strong reciprocators": they are willing to use their personal resources to "be kind to those who are being kind and to punish those who are being unkind", even if they are not certain that their altruistic behaviour will be rewarded [@Fehr2002; @Gachter2009]. This shows that cooperation is not always driven by personal interest and that people care about others' and environment's welfare[@Torsvik2011; @VanVugt2009]. GEF hypothesis: @VonBorgstede2018

In addiction to that, there are evidences suggesting that people do not always thoroughly analyze the context to take a rational cooperative or non-cooperative decision. In fact, cooperation seems to be the intuitive option in social dilemma experiments, while defection needs more thinking [@Kieslich2014]. Moreover, people can also cooperate in part because they are confused about the situation [@Andreoni1995]. In fact, @Fosgaard2017 showed that, in public good games, there is a considerable amount of participants that do not understand correctly the strategies to maximize the personal or the collective payoff. Moreover, these misperceptions can vary depending on how the game is presented.

Therefore, people are not always rational in the economic, individualistic way [@Kollock1998], and there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013]. Understanding how these different factors impact and shape cooperation is therefore essential to try to solve many of the societal problems that we are facing. **???**

## Commons as social dilemmas

Commons are a very specific kind of social dilemma. **FIND A DEFINITION (lol) that shows the similarity with social dilemmas (common resource, ...) !!** + Since, as in social dilemmas, a conflict between individual and collective interest is present @Sussman2016 used the term of "commons dilemmas" to speak about commons.

Predictions about cooperations in commons are also similar to the social dilemma context: according to @Hardin1968 and his "Tragedy of the Commons", since individuals are likely to maximize their individual gain, commons are inevitably destined to failure due to the over exploitation of resources. However, successfully managed commons are often observed [e.g. @Ostrom1990] and, as discussed in the previous section, human beings are not motivated just by their personal interests.

@Franzen2019: example that commons can work (outlets in Swiss farms)

@Reindl2019: cooperation and defection in lab experiments are predictive of behaviours in a real public good (where individuals have to give resources to contribute to a public good)

-   But: Reindl et al. (2019) and Rommel et al. (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
-   @Ros-Galvez2015: those who donated more in a game are those who post more in an online forum (= cooperation)
-   @Sussman2016: at page 11 mention that simulation of commons can be realistic why people feel real emotions (see the articles they cited) "Nevertheless, simulated commons dilemmas do reflect some degree of realism"
-   Importance of commons: Pacheco et al. (2014) having small groups behaving in an ecological way is efficient against climate change  very important to understand under which conditions cooperation could be enhanced in commons
-   @Gomez-Ruiz2020: see part about free-riders in the introduction

@Pacheco2014: "global coordination for a common good should be attempted by segmenting tasks in many small to medium sized groups, in which perception of risk is high and uncertainty in collective goals is minimized"

ideal = decentralized agreements between smaller groups, possibly focused on regional issues are prone to significantly raise the probability of success in coordinating to tame the planet's climate

-   Aim of this scoping review = shed light on cooperation both in social dilemmas and in commons by (1) identifying individual factors that can enhance it and (2) understanding what kind of organization groups can set to improve a cooperation of all members

a.  ?? Is it to mention that I focus on what a group can do, without focusing on how external institutions can influence cooperation?? If so, see @Larsson2016
b.

@@

@Munn2018: reason to conduct a scoping review =\> maybe in the introduction?

To conduct this scoping review, different scientific publications were analyzed in response to the research questions. To gather the papers, a Boolean search methodology was used in different scientific search engines such as Scopus, Web of Science and ScienceDirect. The key phrases were "social dilemma", "public good", "common resource", "commons", "cooperation", "conflicts", "reciprocity", "trust", and they were paired with "AND" and "OR" Boolean operators. The research was made during the month of August, 2023. According with @Munn2022, the type of source was not a selection criteria, therefore journal articles, conference papers and book chapter could be included. This allows us to have an idea as complete as possible about the existing literature on cooperation in commons and social dilemmas. Moreover, there was any chronological or geographical limitation, once again to provide a broader vision of the topic. There were however some selection criteria concerning the papers' methodology and content. First of all, as mentioned in the introduction, this review will focus on individual and group dynamic that can enhance or decrease cooperation in a social dilemma situation (i. e. commons). For this reason, all the papers investigating how an external entity/institution can shape cooperation were not included. Secondly, papers that studied social dilemmas with an agent-based model methodology were also excluded. **include explication** Moreover, in case of experimental or correlative studies, only cases with adult participants were selected.

@@

[^1]: With "experimental studies" are intended all the studies were at least a variable is manipulated by researchers, while "correlational studies" refers to papers using quantitative analysis, but without manipulations.

The papers' topics can be divided in 4 categories: first, "social dilemma setting" (*N*=77) refers to high controlled laboratory experiments where participants have to take cooperative decision. Usually some variables are manipulated to investigate the influence of a specific factor on cooperation [e.g. @Zhang2019]. The type of paradigm used was most of the time a public good game (where participants can decide how much to contribute to a public good, e.g. @Torsvik2011) or a common resource game (where participants can decide how much to take from a common resource, e.g. @Nockur2020). Moreover, the type of game could change vary during the experiment [e.g. @Fosgaard2019]. The second category is "real-life social dilemma situation" (*N*=7), and investigate cooperation in different real-life situations that have a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998]. Thirdly, "real-life commons" (*N*=4) refers to studies that investigate cooperation within participants that are members of a commons in their everyday life. Finally, papers in the category "commons modeled by a social dilemma experiment" (*N*=3) use a laboratory social dilemma paradigm, but with clear references to a concrete common. For instance, in @Mosler1993, participants had to imagine to be fishermen who shared a common basin.

Most of the papers concerned psychology and economic. In fact, thirty-five papers were published in psychology journals, such as *Group Processes & Integroup Relations* or *Psychological Bulletin*, and fourteen in economic journals (e.g. *Experimental Economics*). Additionally, some papers (*N*=8) were published in interdisciplinary journals such as *Journal of Economic Psychology.*

@@

People can also display different levels of trust in the "reliability, effectiveness and legitimacy of public institutions" [@Rompf2017, p.2]. This authors showed that institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied can motivate people to adapt to norms. Moreover, the effects of perceived costs and benefits of the action are less predictive in people with high institutional trust.

@@

There are not many studies on the influence of anonymity on cooperation, but, according to @Wang2017, most of the factors that can increase cooperation rely on a reduction of anonymity. For instance, it is not possible to punish defectors without knowing who they are. Therefore, in general it seems that non-anonymous situations can significantly increase cooperation rates. In fact, when anonymity is removed in a social dilemma situation, cooperation increases and defection is reduced [@Wang2017]. This can be explained by the fact that, when their actions are visible, people worry about others' approval [@Rege2004] and that, in non-anonymous situations, contributions can be a self-presentation strategy, because being perceived as pro-social can increase one's social status [@VanVugt2010a]. There are therefore more social incentives to cooperate in non-anonymous, rather than anonymous, situations.

@@

Reducing anonymity in cooperative interactions can be very effective to encourage people to contribute more. A possible way to do this is to reduce group's size. In fact, according to @Romano2016, a larger group leads to de-individuation, because it is more difficult to understand who is defecting. Therefore, it is easier for members to feel anonymous and to perceive the social punishments associated with defection as less probable. Moreover, communicate is easier in smaller groups [@VonBorgstede2018]. This assumption is confirmed experimentally by @Jiang2021, who showed than in smaller groups people contributed more often to a public good. Increasing cooperation through the reduction of anonymity is also possible by giving public feedbacks about people's cooperation [@Przepiorka2020].

@@

@@

>>>>

During last years, the interest in alternative ways of social organization augmented drastically because of the social and ecological crises we are facing [@Euler2018]. Commons are one of this possible solutions, since they represent an alternative way of organizing resources who does not involve the classic private and public model [@Ostrom1990]. In her seminal work, Ostrom refers to commons (or "common-pool resource") as a resource system equally shared between a self-managed community of users, because of the difficulty of excluding somebody from benefiting from its use [@Ostrom1990]. Beyond the resource aspect of the commons, the notion of social practices (referred as commoning) is also essential [@Euler2018]. Commoning is the process through which people manage to find solutions for their needs by self-organizing independently from the state or the market. Community is therefore engaged in defining rules to successfully manage a shared resource [@Meroni2022], and that is why taking into account the specific community who is commoning is also essential to fully understand a commons [@Dove2019]. @Bollier2019 are even more radical: for them, the term "commons" should not be defined as a resource at all, but as "living social systems" who allow people to self-organize to address shared problems. Finally, "commons can thus be understood as collaborative arrangements for value production processes that are based on participatory principles" [@Seravalli2018a, p. 1].

Commons are currently receiving more and more attention because they function outside of the capitalist system, they respect the Earth by giving mutual benefits to their members [@Meroni2022], and they could be the needed change toward more sustainable and fair economy and society [@Seravalli2018a]. In fact, having small groups with a high perception of risk and a minimal uncertainty in collective goal, possibly focused on regional issues, could significantly improve the probability of success in attaining common goals related to sustainability [@Pacheco2014]. Moreover, it is easier to coordinate on a local, rather than global, level [@Carpenter2011]. Broadly, commons represent a possible solution simply by showing that alternatives to the classic model are possible [@Baibarac-Duignan2023].

However, in order for the commons to be successful its members have to cooperate, i.e to incur a personal sacrifice for the greater good [@Kollock1998], but this cooperation can be difficult to achieve [@Carpenter2011]. This is explained by two characteristics of the commons' social dynamics. First, there is a strong asymmetry, in the sense that the collectivity has a strong impact on the individual, but a person's decisions have a smaller effect on the collective [@Kramer1984]. Therefore, if people are uncertain about others' cooperation, the best solution is pursuing their personal self-interest. Secondly, in a commons situation, every member faces a conflict between individual, short-term interests and collective, long-term ones [@Hardin1968]. For instance, a fisher could be tempted to fish in large quantity from a common basin, but if every other fisher did the same there would not be enough fish for the following seasons. According to @Hardin1968 and his "Tragedy of the Commons", individuals' greed to maximize their personal payoff will inevitably lead to the destruction of the common resource. For these reasons, it is essential to understand why people do (not) cooperate in commons, and which factors can impact cooperation.

## The study of cooperation

It exists different approaches to the study of cooperation. For instance, classical economic theories consider individuals as completely rational and always maximizing (expected) utility [@Edwards1954]. Thus, according to these theories, individuals are not supposed to behave altruistically, namely to incur a personal cost while benefiting others [@Wittek2015]. Another theoretical approach toward cooperation is the evolutionary perspective, who suggests that individuals can show cooperation, but only when doing so bring them a personal advantage. For example, the theory of competitive altruism says that acting for the others' good could be a signal of a person's pro-sociality, and therefore improve this person's reputation [@Roberts1998]. Moreover, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].

Cooperation has also extensively been studied through social dilemma. In such situations, each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do. However, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980]. This approach is very useful to gain insights into how cooperation works because it provides a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].

While economic and evolutionary theories say that individuals are always pursuing their self-interest (either by defecting to maximize their personal payoff, either by cooperating to increase their social status and reputation), social dilemma experiments' results show that it is not always the case. First, it is observed that a significant amount of people are "strong reciprocators": they are willing to use their personal resources to reward cooperators and punish defectors, even if they are not certain that their altruistic behaviour will be rewarded [@Fehr2002; @Gachter2009]. Moreover, according to the Greed Efficiency Fairness hypothesis, people's greed to pursuit their personal interest is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991]. These results shows that cooperation is not always driven by personal interest and that people care about others' and environment's welfare [@Torsvik2011; @VanVugt2009].

In addiction to that, there are evidences suggesting that people do not always thoroughly analyze the context to take a rational decision. In fact, cooperation seems to be the intuitive option in social dilemma experiments, while defection needs more thinking [@Kieslich2014]. Moreover, people can also cooperate in part because they are confused about the situation [@Andreoni1995]. In fact, @Fosgaard2017 showed that, in public good games, there is a considerable amount of participants that do not understand correctly the strategies to maximize the personal or the collective payoff, and these misconceptions can vary depending on how the game is presented. Moreover, there are individual differences in the level of rationality, i.e. the ability to think analytically at the situation [@Lang2018]: individuals scoring low in rationality cooperate more than individuals with an high score. Therefore, people are not always rational in the economic, individualistic way [@Kollock1998], and there are multiple factors that can influence their behaviour in social dilemmas situations [for a review, see @VanLange2013].

## Current review

Like social dilemma experiments challenge economic and evolutionary assumptions about cooperation, so do observations of real-life commons with Hardin's "Tragedy of the Commons": in fact, there are many examples of successful commons [e.g. @Ostrom1990; @Franzen2019]. However, cooperation in commons has not been systematically studied like it has been in social dilemmas, and there is therefore a lack of knowledge about the factors that could enhance cooperation in this context. A way to start to fill this gap is to apply results of social dilemma to the commons. Linking this two topics is pertinent for at least three reasons. First, social dilemmas and commons share the same basic conflict between personal and collective interests [@Hardin1968; @Dawes1980]. For this reason, @Sussman2016 used the term of "commons dilemma" and considered commons to be a particular case of social dilemma. Secondly, cooperation and defection in social dilemma laboratory experiments can predict people's behaviour in a commons situation [e.g. @Reindl2019; @Ros-Galvez2015]. Finally, others studies already used the social dilemma framework to study real-life commons [e.g. @Hartl2022].

Based on these evidences, the aim of the present review is to use social dilemma literature to gain insights into cooperation in commons by (a) identifying individual factors that can shape it and (b) understanding which techniques groups can implement to encourage their members to cooperate. It is important to note that the point (b) will focus exclusively on bottom-up strategies that groups can adopt, and not on top-down solutions like privatization or centralized control of the resource. In fact, it well demonstrated that members of a commons can efficiently manage it without the intervention of an external institution [@Larsson2016]. Moreover, bottom-up solutions are often more efficient than the two others [@Ostrom1990].

@@

Given the exploratory nature of this paper, a scoping review approach is used [@Munn2018]. To conduct it, different scientific publications were analyzed in response to the research questions. To gather the papers, a Boolean search methodology was used in different scientific search engines such as Scopus, Web of Science and ScienceDirect. The key phrases were "social dilemma", "public good", "common resource", "commons", "cooperation", "conflicts", "reciprocity", "trust", and they were paired with "AND" and "OR" Boolean operators. The research was made during the month of August, 2023. According with @Munn2022, the type of source was not a selection criteria, therefore journal articles, conference papers and book chapter could be included. This allows us to have an idea as complete as possible about the existing literature on cooperation in social dilemmas and commons. Moreover, there were not any chronological or geographical limitations, once again to provide a broader vision of the topic. There were however some selection criteria concerning the papers' methodology and content. First, as mentioned in the introduction, papers investigating how an external entity/institution shapes cooperation were not included. Secondly, papers that studied social dilemmas with an agent-based model methodology were also excluded. Moreover, in case of experimental or correlative studies, only cases with adult participants were selected.

@@

[^1]: Studies were at least a variable is manipulated by researchers are part of the category of "experimental studies", while "correlational studies" refers to papers using quantitative analysis, but without manipulations.

The papers' topics can be divided in 4 categories: first, "social dilemma setting" (*N*=77) refers to high controlled laboratory experiments where participants have to take cooperative decision. Usually some variables are manipulated to investigate the influence of a specific factor on cooperation [e.g. @Zhang2019]. The type of paradigm used was most of the time a public good game (where participants can decide how much to contribute to a public good, e.g. @Torsvik2011) or a common resource game (where participants can decide how much to take from a common resource, e.g. @Nockur2020). Moreover, the type of game could vary during the experiment [e.g. @Fosgaard2019]. The second category is "real-life social dilemma situation" (*N*=7), and investigate cooperation in different real-life situations that have a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998]. Thirdly, "real-life commons" (*N*=4) refers to studies that investigate cooperation with participants that are members of a commons in their everyday life. Finally, papers in the category "commons modeled by a social dilemma experiment" (*N*=3) use a laboratory social dilemma paradigm, but with clear references to a concrete common. For instance, in @Mosler1993, participants had to imagine to be fishermen who shared a common basin.

Most of the papers concerned psychology and economy. In fact, thirty-five papers were published in psychology journals, such as *Group Processes & Integroup Relations* or *Psychological Bulletin*, and fourteen in economic journals (e.g. *Experimental Economics*). Additionally, some papers (*N*=8) were published in interdisciplinary journals such as *Journal of Economic Psychology.*

@@

People can also display different levels of trust in the "reliability, effectiveness and legitimacy of public institutions" [@Rompf2017, p. 2]. This authors showed that institutional trust is associated with the probability of recycling, because knowing that sanctions can be efficiently applied can motivate people to adapt to norms. Moreover, the effects of perceived costs and benefits of the action are less predictive in people with high institutional trust.

@@

There are not many studies on the influence of anonymity on cooperation, but, according to @Wang2017, most of the factors that can increase cooperation rely on a reduction of anonymity. For instance, it is not possible to punish defectors without knowing who they are. Therefore, in general it seems that non-anonymous situations can significantly increase cooperation and reduce defection [@Wang2017]. This can be explained by the fact that, when their actions are visible, people worry about others' approval [@Rege2004] and that, in non-anonymous situations, contributions can be a self-presentation strategy, because being perceived as pro-social can increase one's social status [@VanVugt2010a]. There are therefore more social incentives to cooperate in non-anonymous, rather than anonymous, situations.

@@

Reducing anonymity in cooperative interactions can be very effective to encourage people to contribute more. A possible way to do this is to reduce group's size. In fact, according to @Romano2016, a larger group leads to de-individuation, because it is more difficult to understand who is defecting. Therefore, it is easier for members to feel anonymous and to perceive the social punishments associated with defection as less probable. Moreover, communication is easier in smaller groups [@VonBorgstede2018]. This assumption is confirmed experimentally by @Jiang2021, who showed than in smaller groups people contributed more often to a public good. Increasing cooperation through the reduction of anonymity is also possible by giving public feedbacks about people's cooperation [@Przepiorka2020].

@@

This review identified some factors that could impact people's cooperation in social dilemmas and in commons.

-   individual factors: some of them can be manipulated to improve cooperation, some of them must just be taken into account when "planning"

-   group factors = strategies that groups can implement to improve cooperation

-   =\> talk about the practical implication of this (interventions, ...)

Previous theories

Ostrom's (1990) eight principles for successfully managing a common (the 8th not pertinent):

1\. Clearly defined boundaries =\>Individuals or households who have rights to withdraw resource units from the, CPR must be clearly defined, as must the boundaries of the CPR itself. **SOCIAL IDENTITY: since it defines an in-group and an out-group social identity becomes salient** @Tajfel1974

2\. Congruence between appropriation and provision rules and local conditions =\> Appropriation rules restricting time, place, technology, and/or quantity of resource units are related to local conditions and to provision rules requiring labor, material, and/or money.

3\. Collective-choice arrangements =\> Most individuals affected by the operational rules can participate in modifying the operational rules. **COMMUNICATION, SOCIAL NORMS**

4\. Monitoring =\> Monitors, who actively audit CPR conditions and appropriator behavior, are accountable to the appropriators or are the appropriators. **INCENTIVES**

5\. Graduated sanctions =\> Appropriators who violate operational rules are likely to be assessed graduated sanctions (depending on the seriousness and context of the offense) by other appropriators, by officials accountable to these appropriators, or by both. **INCENTIVES**

6\. Conflict-resolution mechanisms =\> Appropriators and their officials have rapid access to low-cost local arenas to resolve conflicts among appropriators or between appropriators and officials. **COMMUNICATION**

7\. Minimal recognition of rights to organize =\> The rights of appropriators to devise their own institutions are not challenged by external governmental authorities. **NOT APPLICABLE BECAUSE NO FOCUS ON EXTERNAL INSTITUTIONS**

At a certain point say that these factors are not independent, but interconnected =\> prepare a model/framework

@Tajfel1974: classic TIS, explanation of why more group identity = more cooperation, see also experiments with minimal groups paradigm

SIMPEA model: [https://www.researchgate.net/profile/Michael-Brenner-Fliesser/publication/368219709/figure/fig2/AS:11431281117565450\@1675469130812/SIMPEA-model-Fritsche-et-al-2018.jpg](https://www.researchgate.net/profile/Michael-Brenner-Fliesser/publication/368219709/figure/fig2/AS:11431281117565450@1675469130812/SIMPEA-model-Fritsche-et-al-2018.jpg)

SIMCA model: [https://www.researchgate.net/profile/Fouad-Bou-Zeineddine/publication/351515886/figure/fig1/AS:1042875005542400\@1625652185052/an-Zomeren-et-al-2008-Social-Identity-Model-of-Collective-Action-SIMCA-with.png](https://www.researchgate.net/profile/Fouad-Bou-Zeineddine/publication/351515886/figure/fig1/AS:1042875005542400@1625652185052/an-Zomeren-et-al-2008-Social-Identity-Model-of-Collective-Action-SIMCA-with.png)

@Chou2013: link between trust and collective efficacy, so that trust could also fit in SIMPEA and SIMCA

bystander effect =\> anonymity

@Aksoy2019: see if class or group had a stronger impact =\> could be a reference to say that it is important to create a common social identity that makes weaker the effect of previous belongings **???**

@Hogg2006: communication and social identity

@Navarro-Carillo2018: high status more generalized trust, low status more in-group depersonalized trust (because more social networks)

@@

social status: low cooperate more than high =\> theories of Iacoviello etc!!!
